Model

### 2019-06-21 stats/kids_novelty.Rmd
correlate model parameters between runs

```{r plot by numerical age}
p5 <- d %>%
  group_by(age_num,experiment, subid) %>%
  summarise(correct = mean(correct))

ggplot(data = p5, aes(x = age_num, y = correct, col = experiment)) +
  geom_smooth(data = d, aes(x = age_num, y = correct),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .3)+
  geom_jitter( alpha = .5, height = 0.01)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion novel item chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized()
```

>>>>

```{r plot by numerical age}
p5 <- d_spin %>%
  group_by(age_num,experiment, subid) %>%
  summarise(correct = mean(correct))

ggplot(data = p5, aes(x = age_num, y = correct, col = experiment)) +
  geom_smooth(data = d_spin, aes(x = age_num, y = correct),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .3)+
  geom_jitter( alpha = .5, height = 0.01)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion novel item chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized()
```

### 2019-06-21 stats/model.Rmd
correlate model parameters between runs

# sem_know_model<- webppl(
#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
#   data = list(data = me_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 8,
#   cores = 8,
#   inference_opts = list(method = "incrementalMH", 
#                         samples = 4000, 
#                         burn = 2000,
#                         verbose = T,
#                         lag = 1,
#                         verboseLag = 1000)
# )

@@

# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
sem_know_model <- readRDS("../saves/sem_know_model.rds")
# 8 chains, 4000 iterations per chain, 2000 burn in, lag = 1
sem_know_model <- readRDS("../saves/sem_know_model_2.rds")
```

@@

### Comparing sem knowledge parameters between model runs

# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
sem_know_run_1 <- readRDS("../saves/sem_know_model.rds")%>%
  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
  filter(parameter == "parameter", type == "items")%>%
  separate(value, into = c("int", "slope"),sep = ", ")%>%
  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
  mutate(run = "1")

# 8 chains, 4000 iterations per chain, 2000 burn in, lag = 1
sem_know_run_2 <- readRDS("../saves/sem_know_model_2.rds")%>%
  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
  filter(parameter == "parameter", type == "items")%>%
  separate(value, into = c("int", "slope"),sep = ", ")%>%
  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
  mutate(run = "2")

sem_know_run_iteration <- bind_rows(
   sem_know_run_1,
   sem_know_run_2)

sem_know_run_summary <- sem_know_run_iteration%>%
  group_by(run,item)%>%
  summarise(overall_int = estimate_mode(int),
            overall_slope = estimate_mode(slope))

sem_know_run <- sem_know_run_iteration %>%
  left_join(sem_know_run_summary)

run_comp <- sem_know_run %>%
  left_join(expand.grid(
      age = unique(me_model_data$age),
      item = unique(me_model_data$familiar)), .) %>%
  mutate(sem_know_ci = plogis(int + slope * age),
         sem_know = plogis(overall_int + overall_slope * age)) %>%
  group_by(run,item, age) %>%
  summarise(sem_know = estimate_mode(sem_know), 
            sem_know_uci = hdi_upper(sem_know_ci),
            sem_know_lci = hdi_lower(sem_know_ci))

ggplot(run_comp, aes(x = age+2, y= sem_know, fill = run))+
  geom_line(size = 1, aes(col = run))+
  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .2)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  ylim(0,1)+
  facet_wrap(~item)+
  theme_few()+
  scale_colour_solarized()+
  scale_fill_solarized()
```

@@

```{r predictions pragmatic model ex 3 adults}
comb_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, combPred , sep='\n'),
  data =list(data = comb_model_data),
  data_var = "dataFromR"
)
# 
# #saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
# #inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
# 
comb_model_predictions <- comb_model_pred %>%
  separate(`0`, into = c("alignment","item", "age"), sep="/")%>%
  mutate(age = as.numeric(age))%>%
  rename( me_effect = `1`)%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         age = age + min(me_data$age_num))
```

>>>>

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 10,
  cores = 10,
  inference_opts = list(method = "incrementalMH",
                        samples = 4000,
                        burn = 2000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

@@

# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
sem_know_model <- readRDS("../saves/run_correlations.rds")#%>%
  # filter(Chain != "15",
  #        Chain != "1",
  #        Chain != "30",
  #        Chain != "6",
  #        Chain != "5",
  #        Chain != "7",
  #        Chain != "3")

@@

### Comparing parameters between model runs

#### sem knowledge

sem_know_run_summary <- item_params%>%
  spread(parameter,value)%>%
  group_by(Chain,item)%>%
  summarise(overall_int = estimate_mode(int),
            overall_slope = estimate_mode(slope))

sem_know_run_iteration <- item_params%>%
  spread(parameter,value)

sem_know_chain <- sem_know_run_iteration %>%
  left_join(sem_know_run_summary)

chain_comp <- sem_know_chain %>%
  left_join(expand.grid(
      age = unique(me_model_data$age),
      item = unique(me_model_data$familiar)), .) %>%
  mutate(sem_know_ci = plogis(int + slope * age),
         sem_know = plogis(overall_int + overall_slope * age)) %>%
  group_by(Chain,item, age) %>%
  summarise(sem_know = estimate_mode(sem_know), 
            sem_know_uci = hdi_upper(sem_know_ci),
            sem_know_lci = hdi_lower(sem_know_ci))

ggplot(chain_comp, aes(x = age+2, y= sem_know, fill = factor(Chain)))+
  geom_line(size = .3, aes(col = factor(Chain)))+
  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .05)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  ylim(0,1)+
  facet_wrap(~item, nrow = 3)+
  theme_few()+
  scale_colour_discrete()+
  scale_fill_discrete()

ggsave("../graphs/model_by_chain.pdf", width = 5, height = 4, scale = 1.5)
```

#### speaker optimality

so_run_iteration <- global_params%>%
  spread(parameter, value)

so_run_summary <- so_run_iteration%>%
  group_by(Chain)%>%
  summarise(overall_int = estimate_mode(int),
            overall_slope = estimate_mode(slope))

so_run <- so_run_iteration %>%
  left_join(so_run_summary)

so_run_comp <-so_run%>%
  group_by(Chain,Iteration)%>%
  expand(int,slope,overall_int,overall_slope,age = unique(me_model_data$age))%>%
  mutate(so_ci = int + slope * age,
         so = overall_int + overall_slope * age) %>%
  group_by(Chain, age) %>%
  summarise(so = estimate_mode(so), 
            so_uci = hdi_upper(so_ci),
            so_lci = hdi_lower(so_ci))

ggplot(so_run_comp, aes(x = age+2, y= so, fill = factor(Chain)))+
  geom_line(size = .4, aes(col = factor(Chain)))+
  geom_ribbon(aes(ymin=so_lci, ymax = so_uci), alpha = .05)+
  ylab("speaker optimality")+
  xlab("Age")+
  #facet_grid(~run)+
  theme_few()+
  scale_colour_discrete()+
  scale_fill_discrete()

ggsave("../graphs/so_by_chain.pdf", width = 4, height = 3, scale = 1.5)
```

#### Correlations between parameters for semantic knowledge

```{r}
# sem_know_model_1<- webppl(
#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
#   data = list(data = me_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 10,
#   cores = 10,
#   inference_opts = list(method = "incrementalMH",
#                         samples = 4000,
#                         burn = 2000,
#                         verbose = T,
#                         lag = 1,
#                         verboseLag = 1000)
# )
# 
# sem_know_model_2<- webppl(
#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
#   data = list(data = me_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 10,
#   cores = 10,
#   inference_opts = list(method = "incrementalMH",
#                         samples = 4000,
#                         burn = 2000,
#                         verbose = T,
#                         lag = 1,
#                         verboseLag = 1000)
# )%>%
#   mutate(Chain = Chain +10)
# 
# sem_know_model_3<- webppl(
#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
#   data = list(data = me_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 10,
#   cores = 10,
#   inference_opts = list(method = "incrementalMH",
#                         samples = 4000,
#                         burn = 2000,
#                         verbose = T,
#                         lag = 1,
#                         verboseLag = 1000)
# )%>%
#   mutate(Chain = Chain +20)
# 
# 
# sem_know_cor_params <- bind_rows(
#   sem_know_model_1,
#   sem_know_model_2,
#   sem_know_model_3
# )%>%
#   saveRDS(.,"../saves/run_correlations.rds")

sem_know_cor_params  <- readRDS("../saves/run_correlations.rds")%>%
  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
  filter(parameter == "parameter", type == "items")%>%
  separate(value, into = c("int", "slope"),sep = ", ")%>%
  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
  gather(parameter, value, int, slope)
 # %>%
#   filter(Chain != "15",
#          Chain != "1",
#          Chain != "30",
#          Chain != "6",
#          Chain != "5",
#          Chain != "7",
#          Chain != "3")

```{r}
ggplot(sem_know_cor_params%>%filter(parameter == "int"), aes(x = value))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(Chain~item, scales = 'free')+
  theme_few()

ggsave("../graphs/item_by_chain.pdf", width = 15, height = 15, scale = 1.5)
```

```{r}
item_params_cor <- sem_know_cor_params %>%
  group_by(Chain,item, parameter)%>%
  summarise(mode = estimate_mode(value))
```

```{r}
library(corrr)
library(corrplot)

## correaltion at 2
cor_int_2 <- item_params_cor%>%
  spread(Chain, mode) %>%
  filter(parameter == "int")%>%
  select(-parameter)%>%
  ungroup()%>%
  select(-item)%>%
  correlate(method = "spearman")%>%
  gather(key, value)%>%
  filter(key !="rowname")%>%
  na.omit()%>%
  mutate(value = as.numeric(value),
         age = "2")

cor_int_3 <- item_params_cor%>%
  spread(parameter, mode)%>%
  mutate(mode = int + slope)%>%
  select(Chain, item, mode)%>%
  spread(Chain, mode)%>%
  ungroup()%>%
  select(-item)%>%
  correlate(method = "spearman")%>%
  gather(key, value)%>%
  filter(key !="rowname")%>%
  na.omit()%>%
  mutate(value = as.numeric(value),
         age = "3")

cor_int_4 <- item_params_cor%>%
  spread(parameter, mode)%>%
  mutate(mode = int + 2*slope)%>%
  select(Chain, item, mode)%>%
  spread(Chain, mode)%>%
  ungroup()%>%
  select(-item)%>%
  correlate(method = "spearman")%>%
  gather(key, value)%>%
  filter(key !="rowname")%>%
  na.omit()%>%
  mutate(value = as.numeric(value),
         age = "4")

cor_int_5 <- item_params_cor%>%
  spread(parameter, mode)%>%
  mutate(mode = int + 3*slope)%>%
  select(Chain, item, mode)%>%
  spread(Chain, mode)%>%
  ungroup()%>%
  select(-item)%>%
  correlate(method = "spearman")%>%
  gather(key, value)%>%
  filter(key !="rowname")%>%
  na.omit()%>%
  mutate(value = as.numeric(value),
         age = "5")

cor_hist <- 
bind_rows(
  cor_int_2,
  cor_int_3,
  cor_int_4,
  cor_int_5
)

ggplot(cor_hist, aes(x = value, fill =age))+
  geom_density(alpha = .5)+
  xlim(-1,1)+
  xlab("Correlation")+
  theme_few()

ggsave("../graphs/corr_int_by_age.pdf", width = 5, height = 4, scale = 1.5)

@@

```{r predictions pragmatic model ex 3 adults}
comb_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, combPred , sep='\n'),
  data =list(data = comb_model_data),
  data_var = "dataFromR"
)
# 
# #saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
# #inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
# 
comb_model_predictions <- comb_model_pred %>%
  separate(`0`, into = c("alignment","item", "age"), sep="/")%>%
  mutate(age = as.numeric(age))%>%
  rename( me_effect = `1`)%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         age = age + min(me_data$age_num))

 tail(comb_model_data)
```
